Initial Analysis

### 2019-11-11 Initial_Analysis.Rmd

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List[1:2],
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

# Save data
# readr::write_csv(Species_Status,
#           "Species_Status.csv")
# head(Species_Status)
```

@@

# Read Sau Catch Data
Sau_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
  filter(!is.na(Territory))

# Read Sau Value Data (Thank you Tim!)
Sau_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
  summarise(Mean_Value = mean(value,na.rm=T))

@@

# Number of Transboundary Species
Total_trans_n <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  ) %>% 
  pull(TaxonKey) %>% 
  length(unique())

@@

Status_Data_Plot <- Tresholded_T_Data %>% 
  mutate(TaxonKey = as.character(TaxonKey)) %>%
  # rename(Territory = CT_fishing_entity) %>% 
  left_join(Species_Status, 
            by =c("Territory","TaxonKey")
  ) %>%
  mutate(Status = ifelse(is.na(Status),"No Status",Status)) %>% 
  group_by(Territory,Status) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,
           group = Georegion,
           observation = Status) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,observation,group,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value))

>>>>

```{r Spp_Status_Sub_Routine, eval = T, echo = F}
# Needs to have trans species 
Species_Status <- bind_rows(
    mclapply(
      Species_List,
      FUN = EstSppStatus,
      Coord = CoorG  # Gabriels coordinate system for read species dist
    )
  )

# Save data
readr::write_csv(Species_Status,
                 paste(Results_Path,"Species_Status.csv",sep="")
                 )
# head(Species_Status)
```

@@

# Read Sau Catch Data
SAU_Catch_Data <- fread(paste(Data_Path,"Distribution_Data/Sau_Catch_Data.csv", sep ="")) %>% 
  filter(!is.na(Territory))

# Read Sau Value Data (Thank you Tim!)
SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  group_by(fishing_entity_id,TaxonKey=taxon_key) %>% 
  summarise(Mean_Value = mean(value,na.rm=T))

@@

# -------------------------- #
# Number of Transboundary Species
# -------------------------- #

Total_trans <- Clean_Results_Trans %>% 
  filter(
    Area_Index >= Min_AI,
    Area_Index <= Max_AI,
    Model_Index >= MI
  )

Total_trans_n <- Total_trans %>% 
  pull(TaxonKey) %>% 
  unique() %>% 
  length()

# -------------------------- #
# Total Revenue
# -------------------------- #

Total_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
  group_by() %>% 
  summarise(Total =sum(Mean_Value)/1000000)# total revenue within EEZs of the world from sau.org

Per_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(TaxonKey %in% Total_trans$TaxonKey) %>% 
  group_by() %>% 
  summarise(Total =sum(Mean_Value)/1000000) %>%  # million
  pull()/160000*100

@@

Status_Data_Plot <- Tresholded_T_Data %>% 
  # mutate(TaxonKey = as.character(TaxonKey)) %>%
  # rename(Territory = CT_fishing_entity) %>% 
  left_join(Status_Data, 
            by =c("Territory","TaxonKey")
  ) %>%
  mutate(Status = ifelse(is.na(Status),"No Status",Status)) %>% 
  group_by(Territory,Status) %>% 
  summarise(value = length(unique(TaxonKey))) %>% 
  left_join(UN_Regions, by ="Territory") %>%
  mutate(Georegion = ifelse(is.na(georegion),"Other",paste(georegion))) %>% 
  rename(FishingRegion=Territory) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(individual = fishing_entity,
           group = Georegion,
           observation = Status) %>% 
  summarise(Total_trans = sum(value,na.rm=T)) %>% 
  mutate(value = ifelse(Total_trans > 100,100,Total_trans)) %>% 
  filter(!is.na(individual)) %>% 
  select(individual,observation,group,value) %>% 
  arrange(group,value) %>% 
  mutate(value = ifelse(observation %in% c("Collapsed","Over Exploited"),value*-1,value))
